Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-05-27 appendix.Rmd
Fix syntax

# read in signficiance from permutation tests (source and target filtered)
icews_sig_all_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target-metric_signif_all.csv", header = FALSE)[-1,-1])
icews_sig_pos_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target-metric_signif_pos.csv", header = FALSE)[-1,-1])
icews_sig_neg_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target-metric_signif_neg.csv", header = FALSE)[-1,-1])

>>>>

# read in signficiance from permutation tests (source and target filtered)
icews_sig_all_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target-metric_signif_all.csv", header = FALSE)[-1,-1])
icews_sig_pos_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target-metric_signif_pos.csv", header = FALSE)[-1,-1])
icews_sig_neg_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target-metric_signif_neg.csv", header = FALSE)[-1,-1])
```

### 2020-05-27 manuscript.Rmd
Fix syntax

# create subdirectories
dir.create("./data/raw") # load three data files here
dir.create("./data/formatted/primary", recursive = TRUE)
dir.create("./data/formatted/secondary/icews", recursive = TRUE)
dir.create("./data/formatted/secondary/phoenix", recursive = TRUE)
dir.create("./results/primary/crqa", recursive = TRUE)
dir.create("./results/primary/windowed-crqa", recursive = TRUE)
dir.create("./results/secondary/icews/crqa/source_target", recursive = TRUE)
dir.create("./results/secondary/icews/crqa/target", recursive = TRUE)
dir.create("./results/secondary/icews/windowed-crqa/source_target", recursive = TRUE)
dir.create("./results/secondary/icews/windowed-crqa/target", recursive = TRUE)
dir.create("./results/secondary/phoenix/crqa/source_target", recursive = TRUE)
dir.create("./results/secondary/phoenix/crqa/target", recursive = TRUE)
dir.create("./results/secondary/phoenix/windowed-crqa/source_target", recursive = TRUE)
dir.create("./results/secondary/phoenix/windowed-crqa/target", recursive = TRUE)

>>>>

# create subdirectories
dir.create("./data/raw") # load three data files here
dir.create("./data/formatted/primary", recursive = TRUE)
dir.create("./data/formatted/secondary/icews", recursive = TRUE)
dir.create("./data/formatted/secondary/phoenix", recursive = TRUE)
dir.create("./results/primary/crqa", recursive = TRUE)
dir.create("./results/primary/windowed-crqa", recursive = TRUE)
dir.create("./results/secondary/icews/crqa", recursive = TRUE)
dir.create("./results/secondary/icews/windowed-crqa", recursive = TRUE)
dir.create("./results/secondary/phoenix/crqa", recursive = TRUE)
dir.create("./results/secondary/phoenix/windowed-crqa", recursive = TRUE)

### 2020-05-27 manuscript.tex
Fix syntax

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{CRQA results for target only data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
\midrule
\endhead
DET & 30.130 & 0.000 & *** & 21.266 & 0.124 & & 25.081 & 0.002 & **\tabularnewline
NRLINE & 85.000 & 0.000 & *** & 61.000 & 0.162 & & 70.000 & 0.008 & **\tabularnewline
maxL & 4.000 & 0.046 & * & 4.000 & 0.057 & . & 5.000 & 0.004 & **\tabularnewline
L & 2.176 & 0.073 & . & 2.148 & 0.193 & & 2.214 & 0.024 & *\tabularnewline
ENTR & 0.493 & 0.058 & . & 0.438 & 0.154 & & 0.538 & 0.036 & *\tabularnewline
rENTR & 0.449 & 0.326 & & 0.399 & 0.444 & & 0.388 & 0.527 &\tabularnewline
LAM & 32.410 & 0.016 & * & 21.591 & 0.252 & & 26.052 & 0.102 &\tabularnewline
TT & 2.187 & 0.186 & & 2.293 & 0.091 & . & 2.368 & 0.036 & *\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{CRQA results for source and target data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
\midrule
\endhead
DET & 28.222 & 0.000 & *** & 23.328 & 0.013 & * & 23.443 & 0.011 & *\tabularnewline
NRLINE & 83.000 & 0.000 & *** & 66.000 & 0.021 & * & 65.000 & 0.023 & *\tabularnewline
maxL & 3.000 & 0.429 & & 4.000 & 0.049 & * & 4.000 & 0.048 & *\tabularnewline
L & 2.084 & 0.708 & & 2.167 & 0.127 & & 2.200 & 0.037 & *\tabularnewline
ENTR & 0.289 & 0.700 & & 0.475 & 0.108 & & 0.523 & 0.033 & *\tabularnewline
rENTR & 0.417 & 0.433 & & 0.432 & 0.381 & & 0.476 & 0.225 &\tabularnewline
LAM & 32.790 & 0.008 & ** & 28.548 & 0.023 & * & 21.639 & 0.201 &\tabularnewline
TT & 2.284 & 0.085 & . & 2.333 & 0.051 & . & 2.129 & 0.298 &\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{verbatim}
## Warning in readLines(x, encoding = "UTF-8"): incomplete final line found on
## 'appendix.Rmd'
\end{verbatim}

@@

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{CRQA results for target only Phoenix data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endhead
DET & 31.065 & 0.246 & & 38.955 & 0.000 & *** & 31.854 & 0.130
&\tabularnewline
NRLINE & 144.000 & 0.220 & & 174.000 & 0.000 & *** & 148.000 & 0.106
&\tabularnewline
maxL & 4.000 & 0.456 & & 5.000 & 0.082 & . & 4.000 & 0.461
&\tabularnewline
L & 2.188 & 0.555 & & 2.270 & 0.030 & * & 2.182 & 0.637 &\tabularnewline
ENTR & 0.513 & 0.527 & & 0.650 & 0.027 & * & 0.504 & 0.615
&\tabularnewline
rENTR & 0.467 & 0.273 & & 0.469 & 0.264 & & 0.459 & 0.344
&\tabularnewline
LAM & 32.051 & 0.290 & & 46.154 & 0.007 & ** & 30.769 & 0.333
&\tabularnewline
TT & 2.273 & 0.211 & & 2.400 & 0.071 & . & 2.400 & 0.073 &
.\tabularnewline
\bottomrule
\end{longtable}

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{CRQA results for source and target Phoenix
data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endhead
DET & 31.558 & 0.168 & & 37.377 & 0.000 & *** & 25.740 & 0.984
&\tabularnewline
NRLINE & 145.000 & 0.172 & & 169.000 & 0.000 & *** & 119.000 & 0.983
&\tabularnewline
maxL & 4.000 & 0.437 & & 5.000 & 0.088 & . & 4.000 & 0.440
&\tabularnewline
L & 2.207 & 0.355 & & 2.243 & 0.125 & & 2.193 & 0.500 &\tabularnewline
ENTR & 0.547 & 0.334 & & 0.610 & 0.100 & . & 0.521 & 0.494
&\tabularnewline
rENTR & 0.498 & 0.164 & & 0.440 & 0.411 & & 0.474 & 0.261
&\tabularnewline
LAM & 38.462 & 0.079 & . & 48.718 & 0.001 & *** & 21.795 & 0.798
&\tabularnewline
TT & 2.500 & 0.021 & * & 2.235 & 0.294 & & 2.429 & 0.042 &
*\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{CRQA results for target only ICEWS data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endhead
DET & 39.250 & 0.000 & *** & 37.870 & 0.000 & *** & 38.659 & 0.000 &
***\tabularnewline
NRLINE & 177.000 & 0.000 & *** & 169.000 & 0.001 & *** & 170.000 & 0.001
& ***\tabularnewline
maxL & 5.000 & 0.074 & . & 5.000 & 0.099 & . & 5.000 & 0.101
&\tabularnewline
L & 2.249 & 0.089 & . & 2.272 & 0.045 & * & 2.306 & 0.009 &
**\tabularnewline
ENTR & 0.619 & 0.080 & . & 0.653 & 0.040 & * & 0.705 & 0.007 &
**\tabularnewline
rENTR & 0.447 & 0.362 & & 0.471 & 0.246 & & 0.509 & 0.125
&\tabularnewline
LAM & 43.590 & 0.017 & * & 39.744 & 0.051 & . & 42.308 & 0.028 &
*\tabularnewline
TT & 2.267 & 0.222 & & 2.385 & 0.093 & . & 2.357 & 0.111
&\tabularnewline
\bottomrule
\end{longtable}

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{CRQA results for source and target ICEWS data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endhead
DET & 34.122 & 0.011 & * & 37.771 & 0.000 & *** & 39.448 & 0.000 &
***\tabularnewline
NRLINE & 152.000 & 0.037 & * & 168.000 & 0.000 & *** & 173.000 & 0.000 &
***\tabularnewline
maxL & 5.000 & 0.090 & . & 5.000 & 0.081 & . & 7.000 & 0.005 &
**\tabularnewline
L & 2.276 & 0.026 & * & 2.280 & 0.024 & * & 2.312 & 0.002 &
**\tabularnewline
ENTR & 0.663 & 0.021 & * & 0.661 & 0.021 & * & 0.698 & 0.005 &
**\tabularnewline
rENTR & 0.478 & 0.236 & & 0.477 & 0.233 & & 0.434 & 0.459
&\tabularnewline
LAM & 34.615 & 0.186 & & 39.744 & 0.045 & * & 48.718 & 0.003 &
**\tabularnewline
TT & 2.250 & 0.236 & & 2.385 & 0.077 & . & 2.235 & 0.267
&\tabularnewline
\bottomrule
\end{longtable}

>>>>

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{CRQA results for target only data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
\midrule
\endhead
DET & 28.525 & 0.000 & *** & 19.672 & 0.288 & & 25.902 & 0.001 & ***\tabularnewline
NRLINE & 80.000 & 0.000 & *** & 57.000 & 0.274 & & 71.000 & 0.005 & **\tabularnewline
maxL & 4.000 & 0.045 & * & 4.000 & 0.053 & . & 4.000 & 0.053 & .\tabularnewline
L & 2.175 & 0.082 & . & 2.105 & 0.474 & & 2.225 & 0.021 & *\tabularnewline
ENTR & 0.481 & 0.079 & . & 0.341 & 0.455 & & 0.575 & 0.015 & *\tabularnewline
rENTR & 0.438 & 0.352 & & 0.311 & 0.749 & & 0.523 & 0.135 &\tabularnewline
LAM & 35.902 & 0.002 & ** & 25.738 & 0.062 & . & 29.344 & 0.021 & *\tabularnewline
TT & 2.147 & 0.238 & & 2.492 & 0.012 & * & 2.295 & 0.049 & *\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{CRQA results for source and target data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
\midrule
\endhead
DET & 25.246 & 0.001 & *** & 21.148 & 0.127 & & 22.623 & 0.023 & *\tabularnewline
NRLINE & 75.000 & 0.000 & *** & 59.000 & 0.193 & & 64.000 & 0.038 & *\tabularnewline
maxL & 3.000 & 0.423 & & 4.000 & 0.036 & * & 3.000 & 0.370 &\tabularnewline
L & 2.053 & 0.911 & & 2.186 & 0.060 & . & 2.156 & 0.155 &\tabularnewline
ENTR & 0.208 & 0.901 & & 0.510 & 0.047 & * & 0.433 & 0.165 &\tabularnewline
rENTR & 0.300 & 0.802 & & 0.464 & 0.255 & & 0.625 & 0.032 & *\tabularnewline
LAM & 34.262 & 0.003 & ** & 27.705 & 0.035 & * & 24.098 & 0.113 &\tabularnewline
TT & 2.247 & 0.107 & & 2.195 & 0.156 & & 2.100 & 0.360 &\tabularnewline
\bottomrule
\end{longtable}

@@

@@

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{CRQA results for target only Phoenix data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endhead
DET & 31.065 & 0.241 & & 38.955 & 0.000 & *** & 31.854 & 0.139
&\tabularnewline
NRLINE & 144.000 & 0.229 & & 174.000 & 0.000 & *** & 148.000 & 0.105
&\tabularnewline
maxL & 4.000 & 0.421 & & 5.000 & 0.087 & . & 4.000 & 0.452
&\tabularnewline
L & 2.188 & 0.544 & & 2.270 & 0.039 & * & 2.182 & 0.580 &\tabularnewline
ENTR & 0.513 & 0.526 & & 0.650 & 0.033 & * & 0.504 & 0.550
&\tabularnewline
rENTR & 0.467 & 0.290 & & 0.469 & 0.276 & & 0.459 & 0.310
&\tabularnewline
LAM & 32.051 & 0.284 & & 46.154 & 0.008 & ** & 30.769 & 0.314
&\tabularnewline
TT & 2.273 & 0.196 & & 2.400 & 0.072 & . & 2.400 & 0.063 &
.\tabularnewline
\bottomrule
\end{longtable}

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{CRQA results for source and target Phoenix
data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endhead
DET & 31.558 & 0.178 & & 37.377 & 0.000 & *** & 25.740 & 0.988
&\tabularnewline
NRLINE & 145.000 & 0.189 & & 169.000 & 0.000 & *** & 119.000 & 0.989
&\tabularnewline
maxL & 4.000 & 0.467 & & 5.000 & 0.084 & . & 4.000 & 0.454
&\tabularnewline
L & 2.207 & 0.368 & & 2.243 & 0.123 & & 2.193 & 0.509 &\tabularnewline
ENTR & 0.547 & 0.343 & & 0.610 & 0.104 & & 0.521 & 0.492
&\tabularnewline
rENTR & 0.498 & 0.135 & & 0.440 & 0.432 & & 0.474 & 0.244
&\tabularnewline
LAM & 38.462 & 0.073 & . & 48.718 & 0.000 & *** & 21.795 & 0.790
&\tabularnewline
TT & 2.500 & 0.017 & * & 2.235 & 0.280 & & 2.429 & 0.048 &
*\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{CRQA results for target only ICEWS data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endhead
DET & 39.250 & 0.000 & *** & 37.870 & 0.000 & *** & 38.659 & 0.000 &
***\tabularnewline
NRLINE & 177.000 & 0.000 & *** & 169.000 & 0.000 & *** & 170.000 & 0.000
& ***\tabularnewline
maxL & 5.000 & 0.093 & . & 5.000 & 0.081 & . & 5.000 & 0.087 &
.\tabularnewline
L & 2.249 & 0.089 & . & 2.272 & 0.033 & * & 2.306 & 0.009 &
**\tabularnewline
ENTR & 0.619 & 0.074 & . & 0.653 & 0.030 & * & 0.705 & 0.008 &
**\tabularnewline
rENTR & 0.447 & 0.368 & & 0.471 & 0.261 & & 0.509 & 0.118
&\tabularnewline
LAM & 43.590 & 0.013 & * & 39.744 & 0.047 & * & 42.308 & 0.030 &
*\tabularnewline
TT & 2.267 & 0.208 & & 2.385 & 0.065 & . & 2.357 & 0.092 &
.\tabularnewline
\bottomrule
\end{longtable}

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{CRQA results for source and target ICEWS data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endhead
DET & 34.122 & 0.014 & * & 37.771 & 0.000 & *** & 39.448 & 0.000 &
***\tabularnewline
NRLINE & 152.000 & 0.064 & . & 168.000 & 0.000 & *** & 173.000 & 0.000 &
***\tabularnewline
maxL & 5.000 & 0.092 & . & 5.000 & 0.093 & . & 7.000 & 0.002 &
**\tabularnewline
L & 2.276 & 0.030 & * & 2.280 & 0.024 & * & 2.312 & 0.003 &
**\tabularnewline
ENTR & 0.663 & 0.022 & * & 0.661 & 0.022 & * & 0.698 & 0.005 &
**\tabularnewline
rENTR & 0.478 & 0.211 & & 0.477 & 0.242 & & 0.434 & 0.475
&\tabularnewline
LAM & 34.615 & 0.178 & & 39.744 & 0.047 & * & 48.718 & 0.002 &
**\tabularnewline
TT & 2.250 & 0.233 & & 2.385 & 0.067 & . & 2.235 & 0.295
&\tabularnewline
\bottomrule
\end{longtable}
